### 2023-12-17 documentation/thesis/thesis_document.tex
more thesis: code listings fix script added

\hypertarget{cli-interface}{%
\subsection{\texorpdfstring{\gls{cli})
Interface}{ Interface}}\label{cli-interface}}

\begin{figure}
\centering
\includegraphics{./generated_images/border_Sensors_CL-Interface.png}
\caption{Sensors CL-Interface \label{Sensors_CL-Interface.png}}
\end{figure}

@@

The figure \ref{MRPlib_Proxy_Module.png} shows the separation of the
various \gls{hal} instances, which communicate with the physically
connected sensors on the \passthrough{\lstinline!remote!}-\gls{pc} and
the \passthrough{\lstinline!control!}-\gls{pc} side, which communicates
with the remote side via the network. For the user, nothing changes in
the procedure for setting up a measurement. The proxy application must
always be started on the \passthrough{\lstinline!remote!} \gls{pc} side.

\begin{lstlisting}[language=bash]
    # START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
    $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B # add another proxy instance http://proxyinstance_2.local for multi-sensor, multi-proxy chain
    Proxy started. http://0.0.0.0:5556/
    PRECHECK: SENSOR_HAL: 1337 # SENSOR A FOUND
    PRECHECK: SENSOR_HAL: 4242 # SENSOR B FOUND
    Terminate  Proxy instance [y/N] [n]: 
\end{lstlisting}

After the proxy instance has been successfully started, it is optionally
possible to check the status via the \gls{rest} interface:

\begin{lstlisting}[language=bash]
    # GET PROXY STATUS
    $ wget http://proxyinstance.local:5556/proxy/status
    {
    "capabilities":[
      "static",
      "axis_b",
      "axis_x",
      "axis_y",
      "axis_z",
      "axis_temp",
      "axis_stimestamp"
   ],
   "commands":[
      "status",
      "initialize",
      "disconnect",
      "combinedsensorcnt",
      "sensorcnt",
      "readsensor",
      "temp"
   ]

@@

The query result shows that the sensors are connected correctly and that
their capabilites have also been recognised correctly. To be able to
configure a measurement on the other, only the \gls{ip} address or host
name of the remote \gls{pc} is required:

\begin{lstlisting}[language=bash]
  # CONFIGURE MEASUREMENT JOB USING A PROXY INSTANCE
  $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B
\end{lstlisting}

@@

\hypertarget{commandline-interface}{%
\section{Commandline interface}\label{commandline-interface}}

\begin{itemize}
\tightlist
\item
  automatische sensor dedettion
\item
  planung verschiedener messungen mit untersch. hardware
\item
  zentrale abarbeitung
\end{itemize}

@@

\begin{lstlisting}
# pipeline_example_measurement_processing.yaml
settings:
 enabled: true
 export_intermediate_results: false
 name: pipeline_example_measurement_processing

stage import_readings:
 function: import_readings
 parameters:
   IP_input_folder: ./readings/fullsphere/
   IP_file_regex: 360_(.)*.mag.json

@@

During the development of the library, test cases were also created for
all important functionalities and use cases. The test framework
\passthrough{\lstinline!PyTest!}\cite{PyTest} was used for this
purpose, as it offers direct integration in most \gls{ide}s (see
\ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
and also because it provides detailed and easy-to-understand test
reports as output in order to quickly identify and correct errors. Since
all intended use cases were mapped using the test cases created, the
code of the test cases could later be used in slightly simplified
variants as examples for the documentation.

\begin{lstlisting}[language=Python]
# $ cat test_mrpreading.py
class TestMPRReading(unittest.TestCase):
    # PREPARE A INITIAL CONFIGURATION FILE FOR ALL FOLLOWING TEST CASES IN THIS FILE
    def setUp(self) -> None:
        self.import_export_test_folderpath: str = os.path.join(os.path.dirname(os.path.abspath(__file__)), "tmp")
        self.import_export_test_filepath:str = os.path.join(self.import_export_test_folderpath, "tmp")

    def test_matrix(self):
        reading: MRPReading = MRPSimulation.MRPSimulation.generate_reading()
        matrix: np.ndarray = reading.to_numpy_matrix()
        n_phi: float = reading.measurement_config.n_phi
        n_theta: float = reading.measurement_config.n_theta
        # CHECK MATRIX SHAPE
        self.assertTrue(matrix.shape != (n_theta, ) and len(matrix.shape) <= n_phi)

    def test_export_reading(self) -> None:
        reading: MRPReading = self.test_reading_init()
        self.assertIsNotNone(reading)
        # EXPORT READING TO A FILE
        reading.dump_to_file(self.import_export_test_filepath)

    def test_import_reading(self):
        # CREATE EMPTY READING
        reading_imported:MRPReading = MRPReading.MRPReading(None)
        # LOAD READING FROM FILE
        reading_imported.load_from_file(self.import_export_test_filepath)
        # CHECK IF ENTRIES ARE POPULATED
        self.assertIsNotNone(reading_imported.additional_data)
        self.assertIsNotNone(reading_imported.data)

if __name__ == '__main__':
    unittest.main()
\end{lstlisting}

@@

One important point that improves usability for users is the simple
installation of the library. As it was created in the Python programming
language, there are several public package directories where users can
provide their software modules. Here,
\passthrough{\lstinline!PyPi!}\cite{PyPI}\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}\cite{MagneticReadoutProcessingPyPI}
is the most commonly used package directory and offers direct support
for the package installation programm \gls{pip}.

@@

\begin{lstlisting}[language=bash]
  # https://pypi.org/project/MagneticReadoutProcessing/
  # install the latest version
  $ pip3 install MagneticReadoutProcessing
  # install the specific version 1.4.0
  $ pip3 install MagneticReadoutProcessing==1.4.0
\end{lstlisting}

@@

Since the library requires additional dependencies
(e.g.~\passthrough{\lstinline!numpy!},
\passthrough{\lstinline!matplotlib!}), which cannot be assumed to be
already installed on the target system, these must be installed prior to
the actual installation. These can be specified in the library
installation configuration \passthrough{\lstinline!setup.py!} for this
purpose.

\begin{lstlisting}[language=Python]
  # $ cat ./setup.py

  # dynamic requirement loading using 'requirements.txt'
  req_path = 'requirements.txt'
  with pathlib.Path(req_path).open() as requirements_txt:
      install_requires = [str(requirement) for requirement in pkg_resources.parse_requirements(requirements_txt)]

  setup(name='MagneticReadoutProcessing',
        version='1.4.3',
        url='https://github.com/LFB-MRI/MagnetCharacterization/',
        packages= ['MRP', 'MRPcli', 'MRPudpp', 'MRPproxy'],
        install_requires=install_requires,
        include_package_data=True,
        package_data={"": ["**/*.mag.json", "**/*.yaml", "**/*.html", "**/*.js", "**/*.css", "**/*.md", "**/*.json", "**/*.ts", "**/*.xml"]},
        entry_points={
            'console_scripts': [
              'MRPCli = MRPcli.cli:run',
              'MRPUdpp = MRPudpp.uddp:run',
              'MRPproxy = MRPproxy.mrpproxy:run'
            ]
        }
      )
\end{lstlisting}

@@

\begin{lstlisting}[language=Python]
    # MRPDataVisualisation.py - example docstring
    def plot_temperature(_readings: [MRPReading.MRPReading], _title: str = '', _filename: str = None, _unit: str = "degree C") -> str:
        """
        Plots a temperature plot of the reading data as bar-graph figure

        :param _readings: readings to plot
        :type _readings: list(MRPReading.MRPReading)

        :param _title: Title text of the figure, embedded into the head
        :type _title: str

        :param _filename: export graphic to an given absolute filepath with .png
        :type _filename: str

        :returns: returns the abs filepath of the generated .png image file
        :rtype: str
        """

        if _readings is None or len(_readings) <= 0:
            raise MRPDataVisualizationException("no readings in _reading given")
        num_readings = len(_readings)
        # ...
\end{lstlisting}

The use of type annotations also simplifies further development, as
modern \gls{ide}s can more reliably display possible methods to the user
as an assistance.

>>>>

\hypertarget{user-interface}{%
\subsection{User-Interface}\label{user-interface}}

\begin{figure}
\centering
\includegraphics{./generated_images/border_Sensors_(+cli).png}
\caption{Sensors \gls{cli} \label{Sensors_(+cli).png}}
\end{figure}

@@

The figure \ref{MRPlib_Proxy_Module.png} shows the separation of the
various \gls{hal} instances, which communicate with the physically
connected sensors on the \passthrough{\lstinline!remote!}-\gls{pc} and
the \passthrough{\lstinline!control!}-\gls{pc} side, which communicates
with the remote side via the network. For the user, nothing changes in
the procedure for setting up a measurement. The proxy application must
always be started\ref{lst:mrpcli_proxy_start} on the
\passthrough{\lstinline!remote!} \gls{pc} side.

\begin{lstlisting}[language=bash, caption={MRPproxy usage to enable local sensor usage over network}, label=lst:mrpcli_proxy_start]
# START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
$ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B # add another proxy instance http://proxyinstance_2.local for multi-sensor, multi-proxy chain
Proxy started. http://remotepc.local:5556/
PRECHECK: SENSOR_HAL: 1337 # SENSOR A FOUND
PRECHECK: SENSOR_HAL: 4242 # SENSOR B FOUND
Terminate  Proxy instance [y/N] [n]: 
\end{lstlisting}

After the proxy instance has been successfully started, it is optionally
possible to check the status via the \gls{rest}
interface:\ref{lst:mrpcli_config_rest}

\begin{lstlisting}[language=bash, caption={MRPproxy REST enpoiint query examples}, label=lst:mrpcli_config_rest]
    # GET PROXY STATUS
    $ wget http://proxyinstance.local:5556/proxy/status
    {
    "capabilities":[
      "static",
      "axis_b",
      "axis_x",
      "axis_y",
      "axis_z",
      "axis_temp",
      "axis_stimestamp"
   ],
   "commands":[
      "status",
      "initialize",
      "disconnect",
      "combinedsensorcnt",
      "sensorcnt",
      "readsensor",
      "temp"
   ]

@@

The query result shows that the sensors are connected correctly and that
their capabilites have also been recognised correctly. To be able to
configure a measurement on the other, only the \gls{ip} address or host
name of the remote \gls{pc} is
required\ref{lst:mrpcli_config_using_rpc}.

\begin{lstlisting}[language=bash, caption={MRPcli usage example to connect with a network sensor}, label=lst:mrpcli_config_using_rpc]
# CONFIGURE MEASUREMENT JOB USING A PROXY INSTANCE
$ MRPcli config setupsensor testcfg --path http://proxyinstance.local:5556
> remote sensor connected: True using proxy connection:
> http://proxyinstance.local:5556 with 1 local sensor connected
\end{lstlisting}

@@

\hypertarget{command-line-interface}{%
\section{Command Line Interface}\label{command-line-interface}}

\begin{figure}
\centering
\includegraphics{./generated_images/border_MRP_(+cli)_output_to_configure_a_new_measurement.png}
\caption{MRP \gls{cli} output to configure a new measurement
\label{MRP_(+cli)_output_to_configure_a_new_measurement.png}}
\end{figure}

In the first version of this library, the user had to write his own
Python scripts even for short measurement and visualisation tasks.
However, this was already time-consuming for reading out a sensor and
configuring the measurement parameters and metadata and quickly required
more than 100 lines of new Python code. Although such examples are
provided in the documentation, it must be possible for programming
beginners in particular to use them. To simplify these tasks, a
\gls{cli}\ref{example_measurement_analysis_pipeline.png} was implemented
around this library, which is then also supplied as a fixed component.
This \gls{cli} implements the following functionalities:

\begin{itemize}
\tightlist
\item
  Detection of connected sensors
\item
  Configuration of measurement series
\item
  Recording of measured values from stored measurement series
\item
  Simple commands for checking recorded measurement series and their
  data.
\end{itemize}

Thanks to this functionality of the \gls{cli}, it is now possible to
connect a sensor to the \gls{pc}, configure a measurement series with it
and run it at the end. The result is then an exported file with the
measured values. These can then be read in again with the library and
processed further. The following\ref{lst:mrpcli_config_run} bash code
shows this procedure in detail:

\begin{lstlisting}[language=bash, caption={CLI example for configuring a measurement run}, label=lst:mrpcli_config_run]
# CLI EXAMPLE FOR CONFIGURING A MEASUREMENT RUN
## CONFIGURE THE SENSOR TO USE
$ MRPcli config setupsensor testcfg
> 0 - Unified Sensor 386731533439 - /dev/cu.usbmodem3867315334391
> Please select one of the found sensors [0]:
> sensor connected: True 1243455
## CONFIGURE THE MEASUREMENT
$ MRPcli config setup testcfg
> CONFIGURE testcfg
> READING-NAME: [testreading]: testreading
> OUTPUT-FOLDER [/cli/reading]: /tmp/reading_folder_path
> NUMBER DATAPOINTS: [1]: 10
> NUMBER AVERAGE READINGS PER DATAPOINT: [1]: 100
# RUN THE CONFIGURED MEASUREMENT
$ MRPcli measure run
> STARTING MEASUREMENT RUN WITH FOLLOWING CONFIGS: ['testcfg']
> config-test: OK
> sensor-connection-test: OK
> START MEASUREMENT CYCLE
> sampling 10 datapoints with 100 average readings
> SID:0 DP:0 B:47.359mT TEMP:23.56
> ....
> dump_to_file testreading_ID:525771256544952_SID:0_MAG:N45_CUBIC_12x12x12.mag.json
\end{lstlisting}

@@

\begin{lstlisting}[caption={Example User Defined Processing Pipeline}]
stage import_readings:
  function: import_readings
  parameters:
    IP_input_folder: ./readings/fullsphere/
    IP_file_regex: 360_(.)*.mag.json

@@

During the development of the library, test cases were also created for
all important functionalities and use cases. The test framework
\passthrough{\lstinline!PyTest!}\cite{PyTest} was used for this
purpose, as it offers direct integration in most \gls{ide}s (see
\ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
and also because it provides detailed and easy-to-understand test
reports as output in order to quickly identify and correct errors. It
also allows to tag tests, which is useful for grouping tests or
excluding certain tests in certain build environment scenarios. Since
all intended use cases were mapped using the test cases created, the
code of the test cases could later be used in slightly simplified
variants\ref{lst:pytest_example_code} as examples for the documentation.

\begin{lstlisting}[language=Python, caption={Example pytest class for testing MRPReading module functions}, label=lst:pytest_example_code]
# $ cat test_mrpreading.py
class TestMPRReading(unittest.TestCase):
  # PREPARE A INITIAL CONFIGURATION FILE FOR ALL FOLLOWING TEST CASES IN THIS FILE
  def setUp(self) -> None:
      self.test_folder: str = os.path.join(os.path.dirname(os.path.abspath(__file__)), "tmp")
      self.test_file:str = os.path.join(self.import_export_test_folderpath, "tmp")

  def test_matrix(self):
      reading: MRPReading = MRPSimulation.generate_reading()
      matrix: np.ndarray = reading.to_numpy_matrix()
      n_phi: float = reading.measurement_config.n_phi
      n_theta: float = reading.measurement_config.n_theta
      # CHECK MATRIX SHAPE
      self.assertTrue(matrix.shape != (n_theta,))
      self.assertTrue(len(matrix.shape) <= n_phi))

  def test_export_reading(self) -> None:
      reading: MRPReading = self.test_reading_init()
      self.assertIsNotNone(reading)
      # EXPORT READING TO A FILE
      reading.dump_to_file(self.test_file)

  def test_import_reading(self):
      # CREATE EMPTY READING
      reading_imported:MRPReading = MRPReading.MRPReading(None)
      # LOAD READING FROM FILE
      reading_imported.load_from_file(self.test_file)
      # CHECK IF ENTRIES ARE POPULATED
      self.assertIsNotNone(reading_imported.additional_data)
      self.assertIsNotNone(reading_imported.data)
\end{lstlisting}

@@

One important point that improves usability for users is the simple
installation of the library. As it was created in the Python programming
language, there are several public package directories where users can
provide their software modules. Here,
\passthrough{\lstinline!PyPi!}\cite{PyPI}\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}\cite{MagneticReadoutProcessingPyPI}
is the most commonly used package directory and offers direct support
for the package installation programm
\gls{pip}\ref{lst:setup_lib_with_pip}.

@@

\begin{lstlisting}[language=bash, caption={Bash commands to install the MagneticReadoutProcessing library using pip}, label=lst:setup_lib_with_pip]
# https://pypi.org/project/MagneticReadoutProcessing/
# install the latest version
$ pip3 install MagneticReadoutProcessing
# install the specific version 1.4.0
$ pip3 install MagneticReadoutProcessing==1.4.0
\end{lstlisting}

@@

Since the library requires additional dependencies
(e.g.~\passthrough{\lstinline!numpy!},
\passthrough{\lstinline!matplotlib!}), which cannot be assumed to be
already installed on the target system, these must be installed prior to
the actual installation. These can be specified in the library
installation configuration
\passthrough{\lstinline!setup.py!}\ref{lst:setup_py_req} for this
purpose.

\begin{lstlisting}[language=Python, caption={setup.py with dynamic requirement parsing used given requirements.txt}, label=lst:setup_py_req]
# dynamic requirement loading using 'requirements.txt'
req_path = './requirements.txt'
with pathlib.Path(req_path).open() as requirements_txt:
    install_requires = [str(requirement) for requirement in pkg_resources.parse_requirements(requirements_txt)]

setup(name='MagneticReadoutProcessing',
      version='1.4.3',
      url='https://github.com/LFB-MRI/MagnetCharacterization/',
      packages= ['MRP', 'MRPcli', 'MRPudpp', 'MRPproxy'],
      install_requires=install_requires,
      entry_points={
          'console_scripts': [
            'MRPCli = MRPcli.cli:run',
            'MRPUdpp = MRPudpp.uddp:run',
            'MRPproxy = MRPproxy.mrpproxy:run'
          ]
      }
    )
\end{lstlisting}

@@

The use of type annotations also simplifies further development, as
modern \gls{ide}s can more reliably display possible methods to the user
as an assistance.\ref{pydocstring}

\begin{lstlisting}[language=Python, caption={Python docstring example}, label=lst:pydocstring]
    # MRPDataVisualisation.py - example docstring
    def plot_temperature(_readings: [MRPReading.MRPReading], _title: str = '', _filename: str = None, _unit: str = "degree C") -> str:
        """
        Plots a temperature plot of the reading data as figure
        :param _readings: readings to plot
        :type _readings: list(MRPReading.MRPReading)
        :param _title: Title text of the figure, embedded into the head
        :type _title: str
        :param _filename: export graphic to an given absolute filepath with .png
        :type _filename: str
        :returns: returns the abs filepath of the generated file
        :rtype: str
        """
        if _readings is None or len(_readings) <= 0:
            raise MRPDataVisualizationException("no readings in _reading given")
        num_readings = len(_readings)
        # ...
\end{lstlisting}
